Draft

### 2021-06-24 SubGroup.Rmd
lancet publication

```{r eval=F}
source("DataWrangling/GlobalOption.R")
source("radiologist.R")
Radiologist <- Radiologist[Radiologist$Referral %in% "MDF", ]

@@

PrivateReferral <-subset(MDF, MDF$UseCase %in% "PrivateReferral")
PublicReferral <-subset(MDF, MDF$UseCase %in% "PublicReferral")
DOTS <-subset(MDF, MDF$UseCase %in% "PublicDOTSRetesting")
WalkIn <-subset(MDF, MDF$UseCase %in% "WalkIn")
Community <-subset(MDF, MDF$UseCase %in% "Community screening")
Contacts <-subset(MDF, MDF$UseCase %in% "Contacts")
# Missing <- subset(MDF, is.na(MDF$UseCase)==T)

New_long <- MDF_long[MDF_long$TB.Medication.History %in% "No",]
Old_long <- MDF_long[MDF_long$TB.Medication.History %in% "Yes",]
Young_long <- MDF_long[MDF_long$AgeGroup %in% "[15,25)",]
Middle_long <- MDF_long[MDF_long$AgeGroup %in% "[25,60)",]
Senior_long <- MDF_long[MDF_long$AgeGroup %in% "[60,108]",]

PrivateReferral_long <-subset(MDF_long, MDF_long$UseCase %in% "PrivateReferral")
PublicReferral_long <-subset(MDF_long, MDF_long$UseCase %in% "PublicReferral")
DOTS_long <-subset(MDF_long, MDF_long$UseCase %in% "PublicDOTSRetesting")
WalkIn_long <-subset(MDF_long, MDF_long$UseCase %in% "WalkIn")
Community_long <-subset(MDF_long, MDF_long$UseCase %in% "Community screening")
Contacts_long <-subset(MDF_long, MDF_long$UseCase %in% "Contacts")
# Missing <- subset(MDF_long, is.na(MDF_long$UseCase)==T)

```{r 2 AUC}
## All
library(precrec)
library(ggplot2)

ROCPRC <- function(dataset){
  attr <- attributes(evalmod(scores = dataset$CAD4TB6, labels = dataset$Xpert2Outcome_num))
  aucT1 <- c("CAD4TB ", round(attr$auc[4],3))

  attr <- attributes(evalmod(scores = dataset$qXRv3, labels = dataset$Xpert2Outcome_num))
  aucT2 <- c("qXR ", round(attr$auc[4],3))

  attr <- attributes(evalmod(scores = dataset$LunitScore, labels = dataset$Xpert2Outcome_num))
  aucT3 <- c("Lunit INSIGHT CXR", round(attr$auc[4],3))

  attr <- attributes(evalmod(scores = dataset$JF1, labels = dataset$Xpert2Outcome_num))
  aucT4 <- c("JF CXR-1", round(attr$auc[4],3))

  attr <- attributes(evalmod(scores = dataset$IF2, labels = dataset$Xpert2Outcome_num))
  aucT5 <- c("InferReadDR ", round(attr$auc[4],3))

@@

## Old on ly
l <- ROCPRC(Old)
Old <- data.frame(matrix(unlist(l), nrow=5, byrow=T))
Old$subgroup <- "Previously treated cases"

@@

colnames(aucTable) <- c("AI.Algorithm", "AUC", "PCAUC", "Subgroup")
write.csv(aucTable, "Results/aucTable.csv")
rm(list=(ls()))
```

```{r ROC AUC with CI}

library(pROC)
ROC <- function(dataset){
  roc_CAD6 <- ci.auc(Xpert2Outcome_num ~ CAD4TB6, dataset)
  roc_qure <- ci.auc(Xpert2Outcome_num ~ qXRv3_100, dataset)
  roc_Lunit <- ci.auc(Xpert2Outcome_num ~ LunitScore_100, dataset)
  roc_JF1 <- ci.auc(Xpert2Outcome_num ~ JF1_100, dataset)
  roc_IF2 <- ci.auc(Xpert2Outcome_num ~ IF2_100, dataset)

@@

## Referral only
Referral <- ROC(Referral)
Referral$subgroup <- "Referred"

@@

## Walk-in only
WalkIn <- ROC(WalkIn)
WalkIn$subgroup <- "WalkIn"

ROCaucTable <- rbind(New, Old, Young, Middle, Senior, Referral, DOTS, WalkIn)
View(ROCaucTable)
write.csv(ROCaucTable, "Results/ROCaucTable.csv", row.names = F)
```

```{r Bar chart}
aucTable <- read.csv("Results/aucTable.csv")
aucTable <- aucTable[, -1]

aucTable$Subgroup <- factor(aucTable$Subgroup, levels = c("All","Young age", "Middle age", "Old age", "PrivateReferral", "PublicReferral", "DOTS", "WalkIn", "Community", "Contacts", "New cases", "Previously treated cases", "Female", "Male"))
### AUC
age<-ggplot(aucTable[aucTable$Subgroup %in% c("Young age", "Middle age", "Old age"), ], aes(x=AI.Algorithm, y=AUC, fill=Subgroup)) +  geom_bar(stat="identity", width=0.6, position=position_dodge())+theme_minimal()+ theme(legend.position = "top")+  ylim(0, 0.95) + theme(panel.grid.minor = element_line(size=0.5)) + scale_y_continuous(minor_breaks = seq(0 , 0.95, 0.05), breaks = seq(0.65, 0.95, 0.05))

referral<-ggplot(aucTable[aucTable$Subgroup %in% c("PrivateReferral", "PublicReferral", "DOTS", "WalkIn", "Community", "Contacts"), ], aes(x=AI.Algorithm, y=AUC, fill=Subgroup)) + geom_bar(stat="identity", width=0.7, position=position_dodge())+theme_minimal()+ theme(legend.position = "top")+  ylim(0, 0.95) + theme(panel.grid.minor = element_line(size=0.5)) + scale_y_continuous(minor_breaks = seq(0 , 0.95, 0.05), breaks = seq(0.65, 0.95, 0.05))

history<-ggplot(aucTable[aucTable$Subgroup %in% c("New cases", "Previously treated cases"), ], aes(x=AI.Algorithm, y=AUC, fill=Subgroup)) + geom_bar(stat="identity", width=0.5, position=position_dodge())+theme_minimal() + theme(legend.position = "top") +  ylim(0, 0.95) + theme(panel.grid.minor = element_line(size=0.5)) + scale_y_continuous(minor_breaks = seq(0 , 0.95, 0.05), breaks = seq(0.65, 0.95, 0.05))

gender <- ggplot(aucTable[aucTable$Subgroup %in% c("Female", "Male"), ], aes(x=AI.Algorithm, y=AUC, fill=Subgroup)) + geom_bar(stat="identity", width=0.5, position=position_dodge())+theme_minimal() + theme(legend.position = "top") +  ylim(0, 0.95) + theme(panel.grid.minor = element_line(size=0.5)) + scale_y_continuous(minor_breaks = seq(0 , 0.95, 0.05), breaks = seq(0.65, 0.95, 0.05))

### PRC
agePC<-ggplot(aucTable[aucTable$Subgroup %in% c("Young age", "Middle age", "Old age"), ], aes(x=AI.Algorithm, y=PCAUC, fill=Subgroup)) +  geom_bar(stat="identity", width=0.6, position=position_dodge())+theme_minimal()+ theme(legend.position = "top")+  ylim(0.3, 0.8) + theme(panel.grid.minor = element_line(size=0.5)) + scale_y_continuous(minor_breaks = seq(0 , 0.8, 0.05), breaks = seq(0.3, 0.8, 0.05))

referralPC<-ggplot(aucTable[aucTable$Subgroup %in% c("PrivateReferral", "PublicReferral", "DOTS", "WalkIn", "Community", "Contacts"), ], aes(x=AI.Algorithm, y=PCAUC, fill=Subgroup)) + geom_bar(stat="identity", width=0.7, position=position_dodge())+theme_minimal()+ theme(legend.position = "top")+  ylim(0.3, 0.8) + theme(panel.grid.minor = element_line(size=0.5)) + scale_y_continuous(minor_breaks = seq(0 , 0.8, 0.05), breaks = seq(0.3, 0.8, 0.05))

historyPC<-ggplot(aucTable[aucTable$Subgroup %in% c("New cases", "Previously treated cases"), ], aes(x=AI.Algorithm, y=PCAUC, fill=Subgroup)) + geom_bar(stat="identity", width=0.5, position=position_dodge())+theme_minimal() + theme(legend.position = "top") +  ylim(0.3, 0.8) + theme(panel.grid.minor = element_line(size=0.5)) + scale_y_continuous(minor_breaks = seq(0 , 0.8, 0.05), breaks = seq(0.3, 0.8, 0.05))

genderPC <- ggplot(aucTable[aucTable$Subgroup %in% c("Female", "Male"), ], aes(x=AI.Algorithm, y=PCAUC, fill=Subgroup)) + geom_bar(stat="identity", width=0.5, position=position_dodge())+theme_minimal() + theme(legend.position = "top") +  ylim(0, 0.95) + theme(panel.grid.minor = element_line(size=0.5)) + scale_y_continuous(minor_breaks = seq(0 , 0.95, 0.05), breaks = seq(0.65, 0.95, 0.05))

tiff("Results/PRC ROC AUC plot 3.tif", width = 20, height = 8, units = "in", res = 110)
require(gridExtra)
grid.arrange(age, referral, history, gender, agePC, referralPC, historyPC, genderPC, ncol=4)
dev.off()

# rm(age, referral, history, agePC, referralPC, historyPC, gender, genderPC)

tiff("Results/PRC AUC plot.tif", width = 9, height = 8, units = "in", res = 100)
grid.arrange(agePC, referralPC, historyPC, genderPC, ncol=2)
dev.off()
```

```{r}
ROCaucTable <- read.csv("Results/ROCaucTable.csv")
ROCaucTable$subgroup <- factor(ROCaucTable$subgroup, levels = c("Young age", "Middle age", "Old age", "Referred", "DOTS retested", "WalkIn", "New cases", "Previously treated cases"))
### AUC
age <-ggplot(ROCaucTable[ROCaucTable$subgroup %in% c("Young age", "Middle age", "Old age"), ], aes(x=AI.Algorithm, y=AUC, fill=subgroup)) +  geom_bar(stat="identity", width=0.6, position=position_dodge()) + geom_errorbar(aes(ymin=AUCL, ymax=AUCH), width=.2, position=position_dodge(0.7)) + theme_minimal()+ theme(legend.position = "top")+  ylim(0, 0.95) + theme(panel.grid.minor = element_line(size=0.5)) + scale_y_continuous(minor_breaks = seq(0 , 0.95, 0.05), breaks = seq(0.65, 0.95, 0.05)) 
age

referral<-ggplot(ROCaucTable[ROCaucTable$subgroup %in% c("Referred", "DOTS retested", "WalkIn"), ], aes(x=AI.Algorithm, y=AUC, fill=subgroup)) + geom_bar(stat="identity", width=0.7, position=position_dodge())+theme_minimal()+ theme(legend.position = "top")+  ylim(0, 0.95) + theme(panel.grid.minor = element_line(size=0.5)) + scale_y_continuous(minor_breaks = seq(0 , 0.95, 0.05), breaks = seq(0.65, 0.95, 0.05)) + geom_errorbar(aes(ymin=AUCL, ymax=AUCH), width=.2, position=position_dodge(0.6)) 
referral

history<-ggplot(ROCaucTable[ROCaucTable$subgroup %in% c("New cases", "Previously treated cases"), ], aes(x=AI.Algorithm, y=AUC, fill=subgroup)) + geom_bar(stat="identity", width=0.5, position=position_dodge())+theme_minimal() + theme(legend.position = "top") +  ylim(0, 0.95) + theme(panel.grid.minor = element_line(size=0.5)) + scale_y_continuous(minor_breaks = seq(0 , 0.95, 0.05), breaks = seq(0.65, 0.95, 0.05)) + geom_errorbar(aes(ymin=AUCL, ymax=AUCH), width=.2, position=position_dodge(0.6))

tiff("Results/ROC_AUC plot.tif", width = 13, height = 3, units = "in", res = 100)
require(gridExtra)

grid.arrange(age, referral, history, ncol=3)

dev.off()
rm(age, referral, history)
```

>>>>

```{r run manually eval=F}
rm(list = ls())

source("DataWrangling/GlobalOption.R")
source("radiologist.R")
Radiologist <- Radiologist[Radiologist$Referral %in% "MDF", ]

@@

PrivateReferral <-subset(MDF, MDF$UseCase %in% "PrivateReferral")
PublicReferral <-subset(MDF, MDF$UseCase %in% "PublicReferral")
DOTS <-subset(MDF, MDF$UseCase %in% "PublicDOTSRetesting")
WalkIn <-subset(MDF, MDF$UseCase %in% "WalkIn")
Community <-subset(MDF, MDF$UseCase %in% "Community screening")
Contacts <-subset(MDF, MDF$UseCase %in% "Contacts")
```

```{r 2 AUCs in subgroups}
## All
library(precrec)
library(ggplot2)

ROCPRC <- function(dataset){
  attr <- attributes(evalmod(scores = dataset$CAD4TB6, labels = dataset$Xpert2Outcome_num))
  aucT1 <- c("CAD4TB ", round(attr$auc[4],4))

  attr <- attributes(evalmod(scores = dataset$qXRv3, labels = dataset$Xpert2Outcome_num))
  aucT2 <- c("qXR ", round(attr$auc[4],4))

  attr <- attributes(evalmod(scores = dataset$LunitScore, labels = dataset$Xpert2Outcome_num))
  aucT3 <- c("Lunit INSIGHT CXR", round(attr$auc[4],4))

  attr <- attributes(evalmod(scores = dataset$JF1, labels = dataset$Xpert2Outcome_num))
  aucT4 <- c("JF CXR-1", round(attr$auc[4],4))

  attr <- attributes(evalmod(scores = dataset$IF2, labels = dataset$Xpert2Outcome_num))
  aucT5 <- c("InferReadDR ", round(attr$auc[4],4))

@@

## Old only
l <- ROCPRC(Old)
Old <- data.frame(matrix(unlist(l), nrow=5, byrow=T))
Old$subgroup <- "Previously treated cases"

@@

colnames(aucTable) <- c("AI.Algorithm", "AUC", "PRAUC", "Subgroup")
write.csv(aucTable, "Results/aucTable.csv")
rm(list=(ls()))
```

```{r ROC AUC with CI}
library(pROC)
ROC <- function(dataset){
  roc_CAD6 <- ci.auc(Xpert2Outcome_num ~ CAD4TB6, dataset)
  roc_qure <- ci.auc(Xpert2Outcome_num ~ qXRv3_100, dataset)
  roc_Lunit <- ci.auc(Xpert2Outcome_num ~ LunitScore, dataset)
  roc_JF1 <- ci.auc(Xpert2Outcome_num ~ JF1, dataset)
  roc_IF2 <- ci.auc(Xpert2Outcome_num ~ IF2, dataset)

@@

## PrivateReferral only
PrivateReferral <- ROC(PrivateReferral)
PrivateReferral$subgroup <- "PrivateReferral"

## PublicReferral only
PublicReferral <- ROC(PublicReferral)
PublicReferral$subgroup <- "PublicReferral"

@@

## WalkIn only
WalkIn <- ROC(WalkIn)
WalkIn$subgroup <- "WalkIn"

## Community only
Community <- ROC(Community)
Community$subgroup <- "Community"

## Contacts only
Contacts <- ROC(Contacts)
Contacts$subgroup <- "Contacts"

## Female only
Female <- ROC(Female)
Female$subgroup <- "Female"

## Male only
Male <- ROC(Male)
Male$subgroup <- "Male"

ROCaucTable <- rbind(New, Old, Young, Middle, Senior, PrivateReferral, PublicReferral, DOTS, WalkIn,Community, Contacts, Female, Male)
View(ROCaucTable)
write.csv(ROCaucTable, "Results/ROCaucTable.csv", row.names = F)
```

```{r Bar chart}
rm(list = ls())

aucTable <- read.csv("Results/aucTable.csv")
aucTable <- aucTable[, -1]

aucTable$Subgroup <- factor(aucTable$Subgroup, levels = c("All","Young age", "Middle age", "Old age", "PrivateReferral", "PublicReferral", "DOTS retested", "WalkIn", "Community", "Contacts", "New cases", "Previously treated cases", "Female", "Male"))
### AUC
# age<-ggplot(aucTable[aucTable$Subgroup %in% c("Young age", "Middle age", "Old age"), ], aes(x=AI.Algorithm, y=AUC, fill=Subgroup)) +  geom_bar(stat="identity", width=0.6, position=position_dodge())+ geom_text(aes(label=AUC), position=position_dodge(width=0.9), vjust=0.05, hjust = 1.5, angle=90)+theme_minimal()+ theme(legend.position = "top")+  ylim(0, 0.95) + theme(panel.grid.minor = element_line(size=0.5)) + scale_y_continuous(minor_breaks = seq(0 , 0.95, 0.05), breaks = seq(0.65, 0.95, 0.05)) 
# 
# 
# referral<-ggplot(aucTable[aucTable$Subgroup %in% c("PrivateReferral", "PublicReferral", "DOTS retested", "WalkIn", "Community", "Contacts"), ], aes(x=AI.Algorithm, y=AUC, fill=Subgroup)) + geom_bar(stat="identity", width=0.7, position=position_dodge())+theme_minimal()+ geom_text(aes(label=AUC), position=position_dodge(width=0.9), vjust=0.05, hjust = 1.5, angle=90)+ theme(legend.position = "top")+  ylim(0, 0.95) + theme(panel.grid.minor = element_line(size=0.5)) + scale_y_continuous(minor_breaks = seq(0 , 0.95, 0.05), breaks = seq(0.65, 0.95, 0.05)) 
# 
# history<-ggplot(aucTable[aucTable$Subgroup %in% c("New cases", "Previously treated cases"), ], aes(x=AI.Algorithm, y=AUC, fill=Subgroup)) + geom_bar(stat="identity", width=0.5, position=position_dodge())+theme_minimal() + geom_text(aes(label=AUC), position=position_dodge(width=0.9), vjust=0.05, hjust = 1.5, angle=90) + theme(legend.position = "top") +  ylim(0, 0.95) + theme(panel.grid.minor = element_line(size=0.5)) + scale_y_continuous(minor_breaks = seq(0 , 0.95, 0.05), breaks = seq(0.65, 0.95, 0.05)) 
# 
# gender <- ggplot(aucTable[aucTable$Subgroup %in% c("Female", "Male"), ], aes(x=AI.Algorithm, y=AUC, fill=Subgroup)) + geom_bar(stat="identity", width=0.5, position=position_dodge())+ geom_text(aes(label=AUC), position=position_dodge(width=0.9), vjust=0.05, hjust = 1.5, angle=90) +theme_minimal() + theme(legend.position = "top") +  ylim(0, 0.95) + theme(panel.grid.minor = element_line(size=0.5)) + scale_y_continuous(minor_breaks = seq(0 , 0.95, 0.05), breaks = seq(0.65, 0.95, 0.05))

### AUC with CI
ROCaucTable <- read.csv("Results/ROCaucTable.csv")
ROCaucTable$AUC <- round(ROCaucTable$AUC, 4)

ROCaucTable$subgroup <- factor(ROCaucTable$subgroup, levels = c("All","Young age", "Middle age", "Old age", "PrivateReferral", "PublicReferral", "DOTS retested", "WalkIn", "Community", "Contacts", "New cases", "Previously treated cases", "Female", "Male"))

age <-ggplot(ROCaucTable[ROCaucTable$subgroup %in% c("Young age", "Middle age", "Old age"), ], aes(x=AI.Algorithm, y=AUC, fill=subgroup)) +  geom_bar(stat="identity", width=0.6, position=position_dodge()) + geom_errorbar(aes(ymin=AUCL, ymax=AUCH), width=.2, position=position_dodge(0.7)) + geom_text(aes(label=AUC), position=position_dodge(width=0.9), vjust=0.05, hjust = 1.5, angle=90) + theme_minimal()+ theme(legend.position = "top")+  ylim(0, 0.95) + theme(panel.grid.minor = element_line(size=0.5)) + scale_y_continuous(minor_breaks = seq(0 , 0.95, 0.05), breaks = seq(0.65, 0.95, 0.05)) 
age

referral<-ggplot(ROCaucTable[ROCaucTable$subgroup %in% c("PrivateReferral", "PublicReferral", "DOTS retested", "WalkIn", "Community", "Contacts"), ], aes(x=AI.Algorithm, y=AUC, fill=subgroup)) + geom_bar(stat="identity", width=0.7, position=position_dodge())+theme_minimal() + geom_text(aes(label=AUC), position=position_dodge(width=0.9), vjust=0.05, hjust = 1.5, angle=90)+ theme(legend.position = "top")+  ylim(0, 0.95) + theme(panel.grid.minor = element_line(size=0.5)) + scale_y_continuous(minor_breaks = seq(0 , 0.95, 0.05), breaks = seq(0.65, 0.95, 0.05)) + geom_errorbar(aes(ymin=AUCL, ymax=AUCH), width=.2, position=position_dodge(0.6)) 
referral

history<-ggplot(ROCaucTable[ROCaucTable$subgroup %in% c("New cases", "Previously treated cases"), ], aes(x=AI.Algorithm, y=AUC, fill=subgroup)) + geom_bar(stat="identity", width=0.5, position=position_dodge())+theme_minimal() + theme(legend.position = "top") +  ylim(0, 0.95) + geom_text(aes(label=AUC), position=position_dodge(width=0.9), vjust=0.05, hjust = 1.5, angle=90)+ theme(panel.grid.minor = element_line(size=0.5)) + scale_y_continuous(minor_breaks = seq(0 , 0.95, 0.05), breaks = seq(0.65, 0.95, 0.05)) + geom_errorbar(aes(ymin=AUCL, ymax=AUCH), width=.2, position=position_dodge(0.6))

gender<-ggplot(ROCaucTable[ROCaucTable$subgroup %in% c("Female", "Male"), ], aes(x=AI.Algorithm, y=AUC, fill=subgroup)) + geom_bar(stat="identity", width=0.5, position=position_dodge())+theme_minimal() + theme(legend.position = "top") +  ylim(0, 0.95) + geom_text(aes(label=AUC), position=position_dodge(width=0.9), vjust=0.05, hjust = 1.5, angle=90)+ theme(panel.grid.minor = element_line(size=0.5)) + scale_y_continuous(minor_breaks = seq(0 , 0.95, 0.05), breaks = seq(0.65, 0.95, 0.05)) + geom_errorbar(aes(ymin=AUCL, ymax=AUCH), width=.2, position=position_dodge(0.6))

### PRC
agePC<-ggplot(aucTable[aucTable$Subgroup %in% c("Young age", "Middle age", "Old age"), ], aes(x=AI.Algorithm, y=PRAUC, fill=Subgroup)) +  geom_bar(stat="identity", width=0.6, position=position_dodge())+ geom_text(aes(label=PRAUC), position=position_dodge(width=0.9), vjust=0.05, hjust = 1.5, angle=90)+theme_minimal()+ theme(legend.position = "top")+  ylim(0.3, 0.8) + theme(panel.grid.minor = element_line(size=0.5)) + scale_y_continuous(minor_breaks = seq(0 , 0.8, 0.05), breaks = seq(0.3, 0.8, 0.05))

referralPC<-ggplot(aucTable[aucTable$Subgroup %in% c("PrivateReferral", "PublicReferral", "DOTS retested", "WalkIn", "Community", "Contacts"), ], aes(x=AI.Algorithm, y=PRAUC, fill=Subgroup)) + geom_bar(stat="identity", width=0.7, position=position_dodge())+ geom_text(aes(label=PRAUC), position=position_dodge(width=0.9), vjust=0.05, hjust = 1.5, angle=90)+theme_minimal()+ theme(legend.position = "top")+  ylim(0.3, 0.8) + theme(panel.grid.minor = element_line(size=0.5)) + scale_y_continuous(minor_breaks = seq(0 , 0.8, 0.05), breaks = seq(0.3, 0.8, 0.05))

historyPC<-ggplot(aucTable[aucTable$Subgroup %in% c("New cases", "Previously treated cases"), ], aes(x=AI.Algorithm, y=PRAUC, fill=Subgroup)) + geom_bar(stat="identity", width=0.5, position=position_dodge())+ geom_text(aes(label=PRAUC), position=position_dodge(width=0.9), vjust=0.05, hjust = 1.5, angle=90)+theme_minimal() + theme(legend.position = "top") +  ylim(0.3, 0.8) + theme(panel.grid.minor = element_line(size=0.5)) + scale_y_continuous(minor_breaks = seq(0 , 0.8, 0.05), breaks = seq(0.3, 0.8, 0.05))

genderPC <- ggplot(aucTable[aucTable$Subgroup %in% c("Female", "Male"), ], aes(x=AI.Algorithm, y=PRAUC, fill=Subgroup)) + geom_bar(stat="identity", width=0.5, position=position_dodge())+ geom_text(aes(label=PRAUC), position=position_dodge(width=0.9), vjust=0.05, hjust = 1.5, angle=90)+theme_minimal() + theme(legend.position = "top") +  ylim(0, 0.95) + theme(panel.grid.minor = element_line(size=0.5)) + scale_y_continuous(minor_breaks = seq(0 , 0.95, 0.05), breaks = seq(0.65, 0.95, 0.05))

# 
# tiff("Results/PRC ROC AUC plot 3.tif", width = 20, height = 8, units = "in", res = 110)
# require(gridExtra)
# grid.arrange(age, referral, history, gender, agePC, referralPC, historyPC, genderPC, ncol=4)
# dev.off()

tiff("Results/Figure3_250.tif", width = 12, height = 14, units = "in", res = 250)
require(gridExtra)
grid.arrange(age, referral, history, gender, agePC, referralPC, historyPC, genderPC, ncol=2)
dev.off()

# tiff("Results/PRC AUC plot.tif", width = 9, height = 8, units = "in", res = 100)
# grid.arrange(agePC, referralPC, historyPC, genderPC, ncol=2)
# dev.off()
```

```{r}
ROCaucTable <- read.csv("Results/ROCaucTable.csv")
ROCaucTable$AUC <- round(ROCaucTable$AUC, 3)

ROCaucTable$subgroup <- factor(ROCaucTable$subgroup, levels = c("All","Young age", "Middle age", "Old age", "PrivateReferral", "PublicReferral", "DOTS retested", "WalkIn", "Community", "Contacts", "New cases", "Previously treated cases", "Female", "Male"))

### AUC with CI
age <-ggplot(ROCaucTable[ROCaucTable$subgroup %in% c("Young age", "Middle age", "Old age"), ], aes(x=AI.Algorithm, y=AUC, fill=subgroup)) +  geom_bar(stat="identity", width=0.6, position=position_dodge()) + geom_errorbar(aes(ymin=AUCL, ymax=AUCH), width=.2, position=position_dodge(0.7)) + geom_text(aes(label=AUC), position=position_dodge(width=0.9), vjust=0.05, hjust = 1.5, angle=90) + theme_minimal()+ theme(legend.position = "top")+  ylim(0, 0.95) + theme(panel.grid.minor = element_line(size=0.5)) + scale_y_continuous(minor_breaks = seq(0 , 0.95, 0.05), breaks = seq(0.65, 0.95, 0.05)) 
age

referral<-ggplot(ROCaucTable[ROCaucTable$subgroup %in% c("PrivateReferral", "PublicReferral", "DOTS retested", "WalkIn", "Community", "Contacts"), ], aes(x=AI.Algorithm, y=AUC, fill=subgroup)) + geom_bar(stat="identity", width=0.7, position=position_dodge())+theme_minimal() + geom_text(aes(label=AUC), position=position_dodge(width=0.9), vjust=0.05, hjust = 1.5, angle=90)+ theme(legend.position = "top")+  ylim(0, 0.95) + theme(panel.grid.minor = element_line(size=0.5)) + scale_y_continuous(minor_breaks = seq(0 , 0.95, 0.05), breaks = seq(0.65, 0.95, 0.05)) + geom_errorbar(aes(ymin=AUCL, ymax=AUCH), width=.2, position=position_dodge(0.6)) 
referral

history<-ggplot(ROCaucTable[ROCaucTable$subgroup %in% c("New cases", "Previously treated cases"), ], aes(x=AI.Algorithm, y=AUC, fill=subgroup)) + geom_bar(stat="identity", width=0.5, position=position_dodge())+theme_minimal() + theme(legend.position = "top") +  ylim(0, 0.95) + geom_text(aes(label=AUC), position=position_dodge(width=0.9), vjust=0.05, hjust = 1.5, angle=90)+ theme(panel.grid.minor = element_line(size=0.5)) + scale_y_continuous(minor_breaks = seq(0 , 0.95, 0.05), breaks = seq(0.65, 0.95, 0.05)) + geom_errorbar(aes(ymin=AUCL, ymax=AUCH), width=.2, position=position_dodge(0.6))

gender<-ggplot(ROCaucTable[ROCaucTable$subgroup %in% c("Female", "Male"), ], aes(x=AI.Algorithm, y=AUC, fill=subgroup)) + geom_bar(stat="identity", width=0.5, position=position_dodge())+theme_minimal() + theme(legend.position = "top") +  ylim(0, 0.95) + geom_text(aes(label=AUC), position=position_dodge(width=0.9), vjust=0.05, hjust = 1.5, angle=90)+ theme(panel.grid.minor = element_line(size=0.5)) + scale_y_continuous(minor_breaks = seq(0 , 0.95, 0.05), breaks = seq(0.65, 0.95, 0.05)) + geom_errorbar(aes(ymin=AUCL, ymax=AUCH), width=.2, position=position_dodge(0.6))

tiff("Results/Figure4.tif", width = 12, height = 7, units = "in", res = 250)
require(gridExtra)
grid.arrange(age, referral, history, gender, ncol=2)
dev.off()
